A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-03-03 sections/model_overview/main.tex
Change vocabulary to be more focused on the application (#33)
* Change vocabulary in game section

* Minor typo

Fix proselint failure by removing the word very from a comment

* Change vocabulary in methodology section

* Additional changes in game section

- Replace waiting zone 1 with hospital
- Replace waiting zone 2 with parking space
- Use type 2 patients everywhere instead of ambulance patients

* Change vocabulary in queueing section

The queueing systems of the hospitals are designed in such a way where they can
accept two types
of individuals. 
% TODO: Decide whether to define type 1, 2 only in game section, only in queueing section, or both
Type 2 individuals are defined as non-urgent patients arriving in ambulances 
that are allocated by the ambulance service and 
type 1 individuals are individuals arriving from other sources 
(e.g walk-in patients, urgent patients from either walk-ins or ambulances).
Each hospital may then choose to block type 2 individuals 
when the hospital reaches a certain capacity. 
The strategy sets for each hospital is the set 
\( \{T \in \mathbb{N} \;|\; 1 \leq T \leq N\} \) where \(N \in\{N_A, N_B\}\) are 
the total capacities of hospitals \(A\) and \(B\). We denote the chosen actions 
from the strategy set as \(T_A, T_B\) and call these \textit{threshold}s.

Both hospitals follow a queueing model with two waiting zones for 
individuals. 
The first waiting zone (i.e. the waiting space of the hospital) is where the 
patients queue right before receiving 
their service and has a queue capacity of \( N - C \), where \(N\) is the total 
capacity of the hospital and \(C\) is the number of servers. 
% TODO: Mention what we mean by servers here?
The second waiting zone (i.e. the parking space for ambulances) is where 
ambulances, that are sent from the
ambulance service, stay until their patients are allowed to enter the hospital.
The parking space has a capacity of \(M\) and no servers.

>>>>

The queueing systems of the hospitals are designed in such a way where they can
accept two types
of individuals. 
Type 2 individuals are defined as non-urgent patients arriving in ambulances 
that are allocated by the ambulance service and 
type 1 individuals are individuals arriving from other sources 
(e.g walk-in patients, urgent patients from either walk-ins or ambulances).
Each hospital may then choose to block type 2 individuals 
when the hospital reaches a certain capacity. 
The strategy sets for each hospital is the set 
\( \{T \in \mathbb{N} \;|\; 1 \leq T \leq N\} \) where \(N \in\{N_A, N_B\}\) are 
the total capacities of hospitals \(A\) and \(B\). We denote the chosen actions 
from the strategy set as \(T_A, T_B\) and call these \textit{threshold}s.

Both hospitals follow a queueing model with two waiting zones for 
individuals. 
The first waiting zone (i.e. the waiting space of the hospital) is where the 
patients queue right before receiving 
their service and has a queue capacity of \( N - C \), where \(N\) is the total 
capacity of the hospital and \(C\) is the number of healthcare 
professionals able to see them.
% TODO: Should this be healthcare professionals or available beds?
The second waiting zone (i.e. the parking space for ambulances) is where 
ambulances, that are sent from the
ambulance service, stay until their patients are allowed to enter the hospital.
The parking space has a capacity of \(M\) and no servers.

### 2022-03-03 sections/queueing_model/proportion_within_target/main.tex
Change vocabulary to be more focused on the application (#33)
* Change vocabulary in game section

* Minor typo

Fix proselint failure by removing the word very from a comment

* Change vocabulary in methodology section

* Additional changes in game section

- Replace waiting zone 1 with hospital
- Replace waiting zone 2 with parking space
- Use type 2 patients everywhere instead of ambulance patients

* Change vocabulary in queueing section

Another performance measure that is taken into consideration is the proportion 
of individuals whose waiting and service times are within a specified 
time target \(t\).
Similar to section \ref{sec:waiting_time}, three formulas are needed for this 
performance measure.

>>>>

Another performance measure that is taken into consideration is the proportion 
of individuals whose time in the hospital (waiting and service time) is within
a specified time target \(t\).
Similar to section \ref{sec:waiting_time}, three formulas are needed for this 
performance measure.
